Let's Get Movin': Frontiers of Optimal Transport

### 2018-04-26 reports/paper/paper.tex
Add LP section to paper

@@

% subsection genetic_algorithms_ (end)
% section inexact_methods (end)

@@

% section applications_ (end)

@@

% section conclusion (end)

>>>>

The \ref{eq:ot_problem} Optimal Transport problem as formulated is an LP. This
means that a natural first-step to benchmarking the problem difficulty is to use
a generic LP solver. The only difficulty we face when doing this is that we must
flatten our arguments from matrices to vectors in order to fit the API of a
generic LP solver, such as \texttt{cvxopt.solvers.lp} which we employ. Recall
that our problem inputs are $\mathbf{a} \in \mathbb{R}^n_{\ge 0}$, $\mathbf{b}
\in \mathbb{R}^m_{\ge 0}$ with sum of entries equal to 1 and $\mathbf{C} \in
\mathbb{R}^{n,m}$. We flatten $C$ into a vector $\mathbf{c} \in \mathbb{R}^{nm}$
and define the matrix
\[ \mathbf{A} := \begin{bmatrix} I_n \otimes \mathbf{1}_m \\ \mathbf{1}_n
\otimes I_m \end{bmatrix} \]
which allows us to formulate our LP as,
\[ \min \mathbf{c}^\top \mathbf{x} \text{ such that } \mathbf{x} \ge 0, \mathbf{A} \mathbf{x} = \begin{bmatrix}
\mathbf{a} \\ \mathbf{b} \end{bmatrix}.\]

We may then benchmark the performance of this data by generating data. We
generate random square $n \times n$ cost matrices by making each entry i.i.d.
$\chi^2(1)$, and perform optimal transport on $\mathbf{a} = \mathbf{b} =
\mathbf{1}_n / n$. The runtimes for different values of $n$ are documented in
\cref{fig:lpruntime}.

\begin{figure}[h]
\includegraphics[width=\textwidth]{../../code/lpruntime}
\caption{Runtime comparison}
\label{fig:lpruntime}
\end{figure}

@@

% subsection genetic_algorithms_ (end)

@@

@@
